An Empirical Analysis of C Preprocessor Use

### 2000-01-18 macros/papers/emp-use-2.tex
Tweak (and move) Greg's edit.

Through extensive discussions, we have found that experts have widely
varying experiences with the preprocessor and similarly varying
expectations about what our data should and do show.  Some of our
specific analyses could have been performed differently, and some can
be (and have been) interpreted in various ways.  Our data, however,
leave little doubt about our high-level views about the broad and
diverse usage of the preprocessor, about the majority of usages being
simple, nor about the potential for reducing at least some of the
complexity introduced by the more complicated uses.

@@

>>>>

Through extensive discussions, we have found that experts have widely
varying experiences with the preprocessor and similarly varying
expectations about what our data should and do show.  Some of our
specific analyses could have been performed differently, and some can
be (and have been) interpreted in various ways.
Our data, however, leave little doubt that the preprocessor is used in
broad and diverse ways, that most of those uses are simple, and that
there is certainly potential to reduce at least some of the complexity
introduced by the more sophisticated uses.

@@

  In \pkg{perl}, unknown identifiers make up 31\% of macro definitions,
  compared to an average of 6.9\% and \verb|ABOUT 9% NEED EXACT NUMBER| in
  \pkg{mosaic}, which has the the second largest proportion of unknown
  identifiers.  In order to avoid link-time collisions when the Perl
  interpreter is embedded in another application, \pkg{perl} conditionally
  redefines over one thousand global symbols to add the prefix
  \verb|Perl_|, as in {\tt \#define Xpv Perl_Xpv}.
